Final Report Semester Project

### 2018-12-13 Visualizations/Draft Visualizations Template.Rmd
Finished summary.

[INSERT PLOT AND INTERPRETATION OF PLOT HERE]

Based off our analysis, it is clear that a significant number of people in the technology workplace have a mental health disorder.  This analysis makes it clear that Human Resource professionals who are interested in expanding outreach need to review their policies regarding requesting leave and protection of employee anonymity when they are handling a mental health issue.  Furthermore, the analysis shows that there is unease among many employees regarding the impact of disclosing a mental health disorder on their career.  Therefore, it is likely necessary to provide training to employees and supervisors with the goal of reducing stigma around mental health.

@@

@@

>>>>

One plot we used in our analysis is the Distribution of Mental health disorders that respondents to the survey had. The visualization and the description of results can also be found in the "Distribution of Mental health disorders" subheading of Section 1.

```{r}
p+xlab("Current Mental health disorders")+ggtitle("Distribution of Mental health disorders currently")
```

As indicated above, mood disorder and anxiety disorder are the most common in our analysis. Furthermore, it is clear that a significant number of people who responded to the survey have at least one mental health disorder.  This analysis makes it clear that Human Resource professionals who are interested in expanding outreach need to review their policies regarding requesting leave and protection of employee anonymity when they are handling a mental health issue.  Furthermore, the analysis shows that there is unease among many employees regarding the impact of disclosing a mental health disorder on their career.  Therefore, it is likely necessary to provide training to employees and supervisors with the goal of reducing stigma around mental health.

@@

Monalisa -

@@

Shruti -
